MSHS COVID-19 Vaccinations

### 2021-05-19 Mimic Historical Arrived and Scheduled Spreadsheet.Rmd
Modify script to summarize doses administered by manufacturer through 3/31/21.

# Import MSSN data from Tableau
mssn_admin <- read_excel(
  path = choose.files(
    default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
    caption = "Select latest MSSN Tableau Administration Data"),
  col_names = TRUE,
  na = c("", NA),
  skip = 1)

@@

colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "AllDoses")
```

@@

# Roll up any Moderna administered at MSB for YWCA to MSH
epic_sched_to_date <- epic_sched_to_date %>%
  mutate(Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site))

@@

# Summarize schedule data for Epic sites by key stratification
epic_sched_summary <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate <= today + 7) %>%
  group_by(Site,
           Dose,
           VaccWeek,
           ApptDate,
           Status2) %>%
  summarize(Count = n(),
            .groups = "keep") %>%
  pivot_wider(names_from = Dose,
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  ungroup()

@@

```{r Format MSSN Tableau data}
# Melt MSSN data to format similar to Epic sites
mssn_admin_to_date <- mssn_admin %>%
  mutate(Site = "MSSN",
         Status2 = "Arr",
         ApptDate = as.Date(ApptDate, format = "%B %d, %Y"),
         VaccWeek = as.numeric(
           floor((ApptDate - vacc_start_first_sun) / 7 +1))) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count")

@@

```{r Combine data across all sites}

# Bind MSSN data with Epic sites data
daily_sched_summary <- rbind(epic_sched_summary, mssn_admin_to_date)

daily_sched_summary <- daily_sched_summary %>%
  left_join(vacc_week_dates, by = c("VaccWeek" = "VaccWeek"))
```

```{r Create and combine tables with vaccine administration and schedule data}
# Create a template of all sites, vaccine dates, and doses ---------
site_rep <- data.frame("Site" = sort(rep(all_sites,
                                         length(doses))))

dose_rep <- data.frame("Dose" = rep(doses,
                                    length(all_sites)))

site_dose_rep <- cbind(site_rep, dose_rep)

site_dose_rep <- site_dose_rep %>%
  mutate(Site = factor(Site, levels = all_sites, ordered = TRUE)) %>%
  arrange(Site, Dose)

# Create a template of this week's days for each site and dose to ensure holidays are included
this_week_prior_days <- all_dates %>%
  filter(VaccWeek == this_week &
           Date < today)

colnames(this_week_prior_days) <- c("ApptDate", "VaccWeek")

this_week_prior_days_rep <- bind_rows(replicate(length(all_sites),
                                              this_week_prior_days,
                                              simplify = FALSE))

site_this_week_prior_days_rep <- data.frame("Site" = sort(
  rep(all_sites, nrow(this_week_prior_days))))

site_this_week_prior_days_templ <- cbind(site_this_week_prior_days_rep,
                                     this_week_prior_days_rep)

site_dose_this_week_prior_days_templ <- left_join(site_dose_rep,
                                                site_this_week_prior_days_templ,
                                                by = c("Site" = "Site"))

# Create template of next 7 days for each site and dose to ensure holidays are included
next_7days <- seq(from = today + 1, to = today + 7, by = 1)

next_7days_rep <- data.frame("ApptDate" = rep(next_7days,
                                          length(all_sites)))

site_next_7days_rep <- data.frame("Site" = sort(rep(all_sites,
                                                    length(next_7days))))

site_next_7days_templ <- cbind(site_next_7days_rep, next_7days_rep)

site_dose_next_7days_templ <- left_join(site_dose_rep,
                                        site_next_7days_templ,
                                        by = c("Site" = "Site"))

# Summarize total doses to date through today -------------
admin_to_date <- daily_sched_summary %>%
  filter(ApptDate <= today) %>%
  group_by(Site, Dose) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

# Summarize administered doses for prior weeks -----------------
prior_weeks_admin <- daily_sched_summary %>%
  filter(VaccWeek < this_week) %>%
  group_by(Site, Dose, VaccWeek, Dates) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = c(VaccWeek, Dates),
              names_prefix = "Wk ",
              names_sep = ": ",
              values_from = AdminDoses)

# Summarize total doses administered and scheduled this week through today -----
this_week_admin_to_date <- daily_sched_summary %>%
  filter(VaccWeek == this_week &
           ApptDate <= today) %>%
  group_by(Site, Dose, VaccWeek, Dates) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup() %>%
  pivot_wider(names_from = c(VaccWeek, Dates),
              names_prefix = "Wk ",
              names_sep = ": ",
              values_from = AdminDoses)

# Summarize data for this week to date -------------------
this_week_daily_admin <- daily_sched_summary %>%
  filter(VaccWeek == this_week &
           ApptDate < today) %>%
  group_by(Site, Dose, ApptDate) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

# Combine with template to ensure holidays are included
this_week_daily_admin <- left_join(site_dose_this_week_prior_days_templ,
                                   this_week_daily_admin,
                                   by = c("Site" = "Site",
                                          "Dose" = "Dose",
                                          "ApptDate" = "ApptDate"))

# Pivot wider to get desired format
this_week_daily_admin <- this_week_daily_admin %>%
  pivot_wider(names_from = c(VaccWeek, ApptDate),
              names_prefix = "Wk ",
              names_sep = c(": "),
              values_from = AdminDoses,
              names_sort = TRUE)

# Summarize today's arrived and scheduled doses -------------
todays_sched <- daily_sched_summary %>%
  filter(ApptDate == today) %>%
  group_by(Site, Dose, ApptDate, Status2) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  pivot_wider(names_from = Status2,
              values_from = AdminDoses) %>%
  mutate(Total = sum(Arr, Sch, na.rm = TRUE),
         VaccWeek = NULL) %>%
  pivot_longer(cols = c(Arr, Sch, Total),
               names_to = "ApptStatus",
               values_to = "Count") %>%
  pivot_wider(names_from = c(ApptDate, ApptStatus),
              names_prefix = "Today's Sched: ",
              values_from = c(Count))

# Summarize scheduled data for the next 7 days ---------------
next_7days_sched <- daily_sched_summary %>%
  filter(ApptDate %in% next_7days) %>%
  group_by(Site, Dose, ApptDate) %>%
  summarize(SchedVisits = sum(Count, na.rm = TRUE),
            .groups = "keep") %>%
  ungroup()

next_7days_sched <- left_join(site_dose_next_7days_templ, next_7days_sched,
                              by = c("Site" = "Site",
                                     "Dose" = "Dose",
                                     "ApptDate" = "ApptDate"))

next_7days_sched <- next_7days_sched %>%
  pivot_wider(names_from = ApptDate,
              values_from = SchedVisits,
              names_sort = TRUE)

# Combine all tables
site_data_summary <- 
  left_join(
    left_join(
      left_join(
        left_join(
          left_join(
            left_join(
              #First, join site and dose template with administered doses to date
              site_dose_rep,
              admin_to_date,
              by = c("Site" = "Site", "Dose" = "Dose")),
            # Second, join with administered doses from prior weeks
            prior_weeks_admin,
            by = c("Site" = "Site", "Dose" = "Dose")),
          # Third, join this week's doses administered/scheduled through today
          this_week_admin_to_date,
          by = c("Site" = "Site", "Dose" = "Dose")),
        # Fourth, join this week's daily data through today
        this_week_daily_admin,
        by = c("Site" = "Site", "Dose" = "Dose")),
      # Fifth, join today's arrived and scheduled appts
      todays_sched,
      by = c("Site" = "Site", "Dose" = "Dose")),
    # Last, join scheduled doses for the next 7 days
    next_7days_sched,
    by = c("Site" = "Site", "Dose" = "Dose"))

# Determine system-wide totals for each dose
system_wide_summary <- do.call(
  #Combine list of dataframes into single dataframe
  rbind, lapply(
    # First, split dataframe into list of dataframes by dose type
    site_data_summary %>%
      group_split(Dose),
    # Next, adorn totals for each dataframe
    function (x)
      x %>%
      adorn_totals(where = "row",
                   fill = unique(x$Dose),
                   na.rm = TRUE,
                   name = "MSHS",
                   -Dose)))
```

```{r Custom function for creating kable}

vaccine_admin_summary <- function(x, dose) {
  # Column Names ---------------
  # Determine date ranges for each week
  weekly_dates <- (vacc_week_dates %>%
                   filter(VaccWeek <= this_week) %>%
                   mutate(Title = paste0("Wk ", VaccWeek, ": ", Dates)))$Title

  # Determine dates this week through yesterday
  # this_weeks_dates <- format(
  # sort(unique(daily_sched_summary %>%
  #               filter(VaccWeek == this_week &
  #                        ApptDate < today) %>%
  #               select(ApptDate))$ApptDate), "%m/%d/%y")

  this_weeks_dates <- format(
    sort((this_week_prior_days %>%
           select(ApptDate))$ApptDate), "%m/%d/%y")

  # Create column names for today's data
  todays_cols <- c(paste(format(today, "%m/%d/%y"), " - Arrived"),
                   paste(format(today, "%m/%d/%y"), " - Later Today"),
                   paste(format(today, "%m/%d/%y"), " - Total"))

  # Create vector with column names
  kable_column_names <- c(colnames(x)[1],
                      "Doses To Date",
                      weekly_dates,
                      this_weeks_dates,
                      todays_cols,
                      format(
                        as.Date(tail(colnames(x), 7), "%Y-%m-%d"), "%m/%d/%y"))

  # Header Names ------------
  # Create header for doses administered each week to date
  weekly_columns_header <- this_week
  names(weekly_columns_header) <- "Adminstered Doses By Week"

  # Create header for this week
  this_week_header <- wday(today) + 2
  names(this_week_header) <- paste("Week", this_week, "To Date")

  # Create header for schedule for next 7 days
  next_7days_header <- 7
  names(next_7days_header) <- "Scheduled Doses Over Next 7 Days"

  # Create vector with header names and length
  kable_headers <- c(" " = 2,
                   weekly_columns_header,
                   this_week_header,
                   next_7days_header)

  kable(x, format = "html", escape = FALSE,
        align = "c", digits = 0,
        col.names = kable_column_names,
        caption = paste0(dose, " Summary")) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           2,
                           this_week + 2,
                           ncol(x) - 10,
                           ncol(x) - 7),
                border_right = "thin solid lightgray") %>%
    column_spec(column = c(3:(this_week + 2)),
                background = sinai_colors[2]) %>%
    column_spec(column = c((this_week + 3):(ncol(x) - 7)),
                background = sinai_colors[4]) %>%
    # include_thead =  TRUE) %>%
    column_spec(column = c((ncol(x) - 6):ncol(x)),
                background = sinai_colors[6]) %>%
    # # include_thead =  TRUE) %>%
    # column_spec(column = c(3:5), background = "inherit", color = "inherit") %>%
    # row_spec(row = 0, background = "#221f72", color = "white") %>%
    row_spec(row = nrow(x), background = "lightgrey",
             bold = T, color = "black") %>%
    add_header_above(kable_headers,
                     background = c("",
                                    sinai_colors[1],
                                    sinai_colors[3],
                                    sinai_colors[5]),
                     line = FALSE,
                     color = "white") %>%
    scroll_box(width = "800px")

@@

#### Administered & Scheduled Vaccines as of `r format(Sys.Date(), "%m/%d/%y")` 3:40PM {.tabset}

##### All Doses
```{r Subset data and create kable for all doses administered}
all_doses <- system_wide_summary %>%
  filter(Dose == "AllDoses") %>%
  mutate(Dose = NULL)

vaccine_admin_summary(x = all_doses, dose = "All Doses")

```
<p></p>

##### First Doses
<p></p>
```{r Subset data and create kable for first doses administered}
first_doses <- system_wide_summary %>%
  filter(Dose == "Dose1") %>%
  mutate(Dose = NULL)

vaccine_admin_summary(x = first_doses, dose = "Dose 1")

<p></p>
##### Second Doses
<p></p>
```{r Subset data and create kable for second doses administered}
second_doses <- system_wide_summary %>%
  filter(Dose == "Dose2") %>%
  mutate(Dose = NULL)

vaccine_admin_summary(x = second_doses, dose = "Dose 2")

>>>>

# Import MSSN data from Tableau
# mssn_employee <- read_excel(
#   path = choose.files(
#     default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
#     caption = "Select MSSN Tableau Administration Data for Employees"),
#   col_names = TRUE,
#   na = c("", NA),
#   skip = 1)
# 
# mssn_nonemployee <- read_excel(
#   path = choose.files(
#     default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
#     caption = "Select MSSN Tableau Administration Data for Non-Employees"),
#   col_names = TRUE,
#   na = c("", NA),
#   skip = 1)
# 
# mssn_employee <- mssn_employee[1:nrow(mssn_employee) - 1, ]
# mssn_nonemployee <- mssn_nonemployee[1:nrow(mssn_nonemployee) - 1, ]
# 
# mssn_employee <- mssn_employee %>%
#   mutate(`Pod Type` = "Employee")
# 
# mssn_nonemployee <- mssn_nonemployee %>%
#   mutate(`Pod Type` = "Patient")
# 
# mssn_admin <- rbind(mssn_employee, mssn_nonemployee)

# Import MSSN data from Tableau
mssn_admin <- read_excel(
  path = choose.files(
    default = paste0(user_directory, "/MSSN Tableau Doses/*.*"),
    caption = "Select MSSN Tableau Administration Data"),
  col_names = TRUE,
  na = c("", NA),
  skip = 1)

@@

colnames(mssn_admin) <- c("ApptDate", "Dose1", "Dose2", "AllDoses")

mssn_admin$Mfg <- "Pfizer"
```

@@

# Update data based on site nuances
epic_sched_to_date <- epic_sched_to_date %>%
  mutate(
    # Roll up any Moderna administered at MSB for YWCA to MSH
    Site = ifelse(Site %in% c("MSB") & Mfg %in% c("Moderna"), "MSH", Site),
    # Update all MSVD visits to J&J
    Mfg = ifelse(Site %in% c("MSVD"), "J&J", Mfg))

@@

# Determine expected manufacturer for scheduled appointments
dose1_moderna <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr") & Mfg == "Moderna" & Dose == "Dose1") %>%
  select(MRN)

epic_sched_to_date <- epic_sched_to_date %>%
  mutate(ExpSchMfg = ifelse(Status2 != "Sch", NA,
                            ifelse(Site == "MSVD", "J&J",
                                   ifelse(Dose == 'Dose1', "Pfizer",
                                          ifelse(MRN %in% dose1_moderna$MRN,
                                                 "Moderna", "Pfizer")))),
         MfgRollUp = ifelse(is.na(Mfg) & is.na(ExpSchMfg), NA,
                            ifelse(is.na(ExpSchMfg), Mfg, ExpSchMfg)))

# Summarize schedule data for Epic sites by key stratification
epic_sched_summary <- epic_sched_to_date %>%
  filter(Status2 %in% c("Arr", "Sch") &
           ApptDate <= today) %>%
  group_by(Site,
           MfgRollUp,
           Dose,
           VaccWeek,
           ApptDate,
           Status2) %>%
  summarize(Count = n(),
            .groups = "keep") %>%
  pivot_wider(names_from = Dose,
              values_from = Count) %>%
  mutate(AllDoses = sum(Dose1, Dose2, na.rm = TRUE)) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count") %>%
  ungroup()

test_df <- epic_sched_summary %>%
  filter(ApptDate <= today) %>%
  group_by(Site, Dose) %>%
  summarize(Admin = sum(Count, na.rm = TRUE))

@@

```{r Format MSSN Tableau data}
# Melt MSSN data to format similar to Epic sites
mssn_admin_to_date <- mssn_admin %>%
  mutate(Site = "MSSN",
         Status2 = "Arr",
         ApptDate = as.Date(ApptDate, format = "%B %d, %Y"),
         VaccWeek = as.numeric(
           floor((ApptDate - vacc_start_first_sun) / 7 +1)),
         MfgRollUp = Mfg) %>%
  filter(ApptDate <= today) %>%
  pivot_longer(cols = c("Dose1", "Dose2", "AllDoses"),
               names_to = "Dose",
               values_to = "Count")

@@

```{r Combine data across all sites}
# Bind MSSN data with Epic sites data
daily_sched_summary <- rbind(epic_sched_summary, mssn_admin_to_date)

daily_sched_summary <- daily_sched_summary %>%
  left_join(vacc_week_dates, by = c("VaccWeek" = "VaccWeek"))

admin_doses_by_mfg <- daily_sched_summary %>%
  group_by(Site, Dose, MfgRollUp) %>%
  summarize(AdminDoses = sum(Count, na.rm = TRUE))

write_xlsx(admin_doses_by_mfg, path = paste0(user_directory,
                                             "/AdHoc/Admin Doses By Mfg Through 03312021.xlsx"))

@@
